---
title: "HER Patient Sampling Report"
author: "Mohammad Farhad Sahebi"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: flatly
  pdf_document:
    toc: true
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
library(readxl)
library(dplyr)
library(kableExtra)
library(ggplot2)
library(skimr)
```

# 1. Introduction

This report provides an overview and basic analysis of the HER patient sampling dataset.

# 2. Importing the data

```{r load-data}
setwd("C:/Users/Dell/Downloads/Patient Sample Script")

samples <- read_excel("HER pat sampling23_11_25.xlsx")

head(samples) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

# 3. Data Structure and Summary

```{r structure}
str(samples)
skimr::skim(samples)
```

# 4. Key Variables

```{r key-vars}
samples %>%
  select(Province, `Health Facility Name`, Site_Visit_ID) %>%
  head(20) %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

# 5. Summary by Province

```{r province-summary}
prov_summary <- samples %>%
  group_by(Province) %>%
  summarise(n = n())

prov_summary %>%
  kable(col.names = c("Province", "Number of Samples")) %>%
  kable_styling(full_width = FALSE)
```

```{r province-plot}
ggplot(prov_summary, aes(x = reorder(Province, n), y = n)) +
  geom_col(fill = "#2E86C1", width = 0.7) +
  geom_text(aes(label = n), vjust = -0.4, size = 4.2, fontface = "bold") +
  labs(
    title = "📊 Samples Collected by Province",
    subtitle = "HER Patient Sampling — Facility-level distribution",
    x = "Province",
    y = "Number of Samples",
    caption = "Prepared by Mohammad Farhad Sahebi — Data Analyst"
  ) +
  theme_minimal(base_family = "Calibri") +
  theme(
    plot.title = element_text(size = 18, face = "bold", color = "#1A5276"),
    plot.subtitle = element_text(size = 13, face = "plain", color = "#424949"),
    axis.text.x = element_text(size = 12, angle = 25, hjust = 1, face = "bold"),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 13, face = "bold"),
    panel.grid.major.y = element_line(color = "#D5D8DC"),
    panel.grid.minor = element_blank(),
    plot.caption = element_text(size = 10, color = "gray40", face = "italic")
  )

```

# 6. Summary by Health Facility

```{r hf-summary}
hf_summary <- samples %>%
  group_by(`Health Facility Name`) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

hf_summary %>%
  head(20) %>%
  kable(col.names = c("Health Facility", "Number of Samples")) %>%
  kable_styling(full_width = FALSE)
```

# 7. Sample Site View

```{r one-site}
one_site <- samples %>%
  filter(Site_Visit_ID == samples$Site_Visit_ID[1])

one_site %>%
  kable() %>%
  kable_styling(full_width = FALSE)
```

# 8. Conclusion

This report:

- Loaded the dataset  
- Explored structure and variables  
- Displayed summary statistics  
- Generated visualizations  
- Demonstrated site-level detail  

Further development can include:

- rejection rate analysis  
- interviewer performance  
- geographic mapping  
- facility-wise sample quality scoring  
